---
title: "Title of the Bachelor Thesis"
subtitle: "Kickoff for Bachelor Thesis"
author: "Zolbayasakh Tsoggerel"
authorshort: z.tsoggerel@hci-kdd.org
date: "Graz, April 14, 2015"
output:
  beamer_presentation:
    colortheme: holzinger
    fig_caption: yes
    fonttheme: professionalfonts
    highlight: tango
    keep_tex: yes
    pandoc_args:
    - --listings
    - --biblatex
    slide_level: 2
    template: config/template.beamer
    theme: holzinger
    toc: no
csl: config/elsevier-harvard.csl
bibliography: references.bib
address: Holzinger Group - hci-kdd.org
---
```{r, include=FALSE}
source('config/knitr-settings.R')
```

# You type a title like this

<!-- if there is no subtitle you need write "----" to start a slide -->

----

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

# You can also include static images (don't forget to reference the source)

----

!["Significant" - [http://xkcd.com/882/](http://xkcd.com/882/)](images/jellybeans3.png)

# R Markdown 2

## Slide with Bullets

- Bullet 1

- Bullet 2

- Bullet 3

## Slide with some references

<!-- note that references will only be included if you run the ./buildSlides script -->
<!-- The @reference references need to be in the references.bib file -->

**The DUKE saga** [^starter]: *"Genomic signatures to guide the use of chemotherapeutics"*

- Flawed data analysis by Potti *et al.*[@potti2006genomic] 
    
- Made it into clinical trials!
    
- Baggerly and Coombes[@baggerly2009deriving] were the researches that 
  spotted the flaw

[^starter]: http://simplystatistics.org/2012/02/27/the-duke-saga-starter-set/

# Slide with R Code and Output

----

```{r, results='asis'}
pander(head(mtcars[,1:6]))
```

# Slide with an R Plot and hidden code

----

```{r examplePlot, echo=FALSE, fig.cap="This is my figure"}
qplot(speed, dist, data = cars) + geom_smooth(method="lm")
```

